---
title: "Week 6 Assignment"
author: "Richard Rachman"
date: "2021/03/03"
output:
  tufte::tufte_html:
  html_document:
    toc: yes
 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```




## **Libraries**
```{r}
library(palmerpenguins)
library(tidyverse)
library(here)
library(kableExtra)
library(tufte)
library(viridis)
```

### *Notes for lab*

* Take any of the data sheets you have already worked with in class and create at least one table and one figure in an Rmarkdown file.  
* Create the most beautiful RMarkdown output you can during lab hours in either an html, github doc, or pdf format.    
* Make sure you have headings with clear explanations of what you are doing.    
- Practice using markdown formatting with bold, italics, and lists.  
* Make sure your outputs and scripts are saved in the appropriate folders. Keep proper coding etiquette (figures need to be pub quality as usual).

## **Data**

```{r}
View(penguins)
```

## **Script**
### We are first going to change the name of the sexes in the data, then seperate males and females to get our desired graph for specifically Adelie penguins. 

```{r}


penguins <- penguins %>% mutate(sex = fct_recode(sex, 
                                                 "Male" = "male", 
                                                 "Female" = "female"))

penguins %>% filter(sex == "Male" | sex == "Female") %>% 
  filter(species == "Adelie") %>% 
  ## Separate males and females
  ggplot(aes(x=sex, y=body_mass_g, fill=sex)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
  geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white", color = "white"),
        legend.position="none",
        plot.title = element_text(size=20)
  ) +
  facet_grid(~island) + 
  labs(y="Body Mass (g)", x="Sex", 
       title="Adelie Penguins Body Mass by Island")
```



